Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-03-10 lqg-strings.tex
Updated abstract, started work on explaining gauged Polyakov action

\begin{abstract}
	With the goal of understanding whether or not it is possible to construct a string theory which is consistent with loop quantum gravity (LQG), we study alternate versions of the Nambu-Goto action for a Bosonic string. We consider two types of modifications. The first is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geoemtry and are bounded from below. The second is an action in which the background geometry is described in terms of a vielbein $E^\mu_I$ and a connection field $A_\mu^{IJ}$, in the spirit of LQG. The modified Nambu-Goto action is constructed by pulling back the background connection onto the worldsheet and replacing ordinary partial derivatives by covariant derivatives with respect to the pulled back conection $\mc{A}_a^{IJ}$.
\end{abstract}

@@

\begin{equation}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}
Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

@@

>>>>

\begin{abstract}

	With the goal of understanding whether or not it is possible to construct a string theory which is consistent with loop quantum gravity (LQG), we study alternate versions of the Nambu-Goto action for a bosonic string. We consider two types of modifications. The first is a phenomenological action based on the observation that LQG tells us that areas of two-surfaces are operators in quantum geometry and are bounded from below. This leads us to a string action which is similar to that of bimetric gravity. We provide formulations of the bimetric string for both the Nambu-Goto (second order) and Polyakov (first order) formulations. We explore the classical solutions of this action and its quantization and relate it to the conventional string solutions.

	The second is an action in which the background geometry is described in terms of the pullback of the connection which describes the bulk geometry to the worldsheet. The resulting action is in the form of a gauged sigma model, where the spacetime co-ordinates are now SO(D,1) vectors. We find that for the particular case of a constant background connection the action reduces to the bimetric action discussed above. We discuss classical solutions and quantization strategies for this action and its implications for the broader program of unifying string theory and loop quantum gravity.
\end{abstract}

@@

\begin{equation}\label{eqn:polyakov-action}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}

Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

@@

First let us recall the form of the Polyakov action for the bosonic string \eqref{eqn:polyakov-action}:

\begin{equation*}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation*}

If one was to ask a beginning graduate student as to how one can incorporate a gauge field in the above expression, the natural answer would be that we can promote the $X^\mu$ to vectors which live in the representation of some gauge group $\mc G$ and promote the ordinary derivative to a gauge covariant derivative \wrt a connection valued in $\mc G$. The resulting action would now have the form:

\begin{equation}\label{eqn:polyakov-gauged}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \mc{D}_a X^\mu \mc{D}_b X^\nu \eta_{\mu\nu},
\end{equation}

where the covariant derivative $\mc{D}_a$ is of the form:
\begin{equation}\label{eqn:covariant-deriv}
	\mc{D}_a X^\mu(\tau , \sigma) = \partial_a X^\mu + g \mc{A}_{a}^\mu{}_\nu X^\nu,
\end{equation}
where $\mc{A}_{a}^\mu{}_\nu$ is the gauge field and $g$ is the gauge coupling. A more experienced researcher would object saying that we know that the $X^\mu$ are spacetime co-ordinates and not vectors transforming
